Supernovae Time Profiles as a Probe of New Physics at Neutrino Telescopes

### 2024-02-21 paper/sections/preamble.tex
Updates from Overleaf

\preprint{APS/123-QED, USTC-ICTS/PCFT-24-xx}
\bibliographystyle{apsrev4-1}
\title{
% New Physics in Supernovae at Neutrino Telescopes
% Time Prints of New Physics from Supernovae at Neutrino Telescopes
% Supernova Detection with Neutrino Telescopes as a Portal to New Physics
Supernovae Time Profiles as a Portal to New Physics at Neutrino Telescopes
}

@@

\begin{abstract}
Neutrino telescopes, such as IceCube, have promised precise time resolutions at the millisecond level for detecting collective rise signals in all photomultiplier.
We demonstrate that such precise time resolutions will play a crucial role in tracking neutrino signals with novel timing patterns related to weakly interacting massive particles in physics beyond the Standard Model.
Focusing on a future Supernova explosion in the operation time of IceCube as an example, we show that neutrino telescopes can provide unprecedented probes of new particles with both low and high masses from probing early-glow and after-glow neutrino signals, respectively, while comparable to DUNE and Hyper-K in the intermediate mass region.
\end{abstract}

>>>>

\preprint{USTC-ICTS/PCFT-24-07, APS/123-QED}
\bibliographystyle{apsrev4-1}
\title{
% New Physics in Supernovae at Neutrino Telescopes
% Time Prints of New Physics from Supernovae at Neutrino Telescopes
% Supernova Detection with Neutrino Telescopes as a Portal to New Physics
Supernovae Time Profiles as a Probe of New Physics at Neutrino Telescopes
}

@@

\begin{abstract}
Neutrino telescopes, including IceCube, can detect galactic supernova events by observing the collective rise in photomultiplier count rates with a sub-second time resolution. Leveraging precise timing, we demonstrate for the first time the capability of neutrino telescopes to explore new weakly coupled states emitted from supernovae and subsequently decaying to neutrinos. Our approach utilizes publicly available packages, \texttt{ASTERIA} and \texttt{SNEWPY}, for simulating detector responses and implementing neutrino fluxes originated from Standard Model and new physics. We present results for two new physics models
employing a specific supernova model and introduce the tool developed for testing a diverse range of new physics models.
\end{abstract}
